Rotations and Insecticide Resistance the story

### 2019-06-14 inst/documents/rotations_notes.Rmd
tidying

12/03/19
~ change origin of git repo in RStudio, probably need to do from git
remote: This repository moved. Please use the new location:        
remote:   git@github.com:AndySouth/rotations.git    
from the commandline :
git remote rm origin
git remote add origin git@github.com:AndySouth/rotations.git

>>>>

#12/03/19
~ change origin of git repo in RStudio, probably need to do from git
remote: This repository moved. Please use the new location:        
remote:   git@github.com:AndySouth/rotations.git    
from the commandline :
git remote rm origin
git remote add origin git@github.com:AndySouth/rotations.git

#14/06/2019
Testing before sending to Sam.
Error in mortRR["f", "intervention"] : incorrect number of dimensions

This is when coverage set to 1, because there is no intervention dimension in mortRR[] in run_tot()

fixed

then got this from the script because it is trying to cast a tibble with an insecticide column and gens to a number
Error: (list) object cannot be coerced to type 'double'

so I modified gens_under_thresh() to just return the numeric column

BUT this doesn't solve and I don't know why this problem appeared when it wasn't there before ???

gens_under_thresh() is giving one row per insecticide, is that what I'm expecting ??
No it is supposed to be :
'the sum across all insecticides for the number of generations below threshold while that insecticide is deployed'

so why has it changed ?? BUG introduced by the mortality addition
##14/6/19 corrected bug here by adding back res <-      
res <- summarise(res, tot_gens_dep_under50 = sum(.data$gens_dep_under50)) %>%
